\large Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-12 Dissertation/Defense/defense.tex
added exploration parts, still need patrol, 2D & 3D NRL tests (mostly copy), and 3D exploration (new)

@@

\begin{frame}
\frametitle{Publications}
{\tiny 
\begin{itemize}
	\item E. Kaufman, K. Takami, T. Lee, and Z. Ai, ``Autonomous Exploration with Exact Inverse Sensor Models,'' \textit{Journal of Intelligent }\&\textit{ Robotic Systems}, 2016, submitted.
	\item E. Kaufman, T. Lee, and Z. Ai, ``Autonomous Exploration by Expected Information Gain from Probabilistic Occupancy Grid Mapping,'' \textit{IEEE International Conference on Simulation, Modeling, and Programming for Autonomous Robots}, San Francisco, December 2016, accepted.
	\item E. Kaufman, T. Lee, Z. Ai, and I. S. Moskowitz, ``Bayesian Occupancy Grid Mapping via an Exact Inverse Sensor Model,'' \textit{Proceedings of the American Control Conference}, Boston, July 2016, pp. 5709-5715.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Nonlinear Observability Measure for Relative Orbit Determination with Angles-Only Measurements,'' \textit{The Journal of the Astronautical Sciences}, 63(1): pp. 60-80, 2016, doi: 10.1007/s40295-015-0082-9.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Minimum Uncertainty JPDA Filters and Coalescence Avoidance for Multiple Object Tracking,'' \textit{The Journal of the Astronautical Sciences}, 63(4): pp. 308-334, 2016, doi: 10.1007/s40295-016-0092-2.
	\item T. Wu, E. Kaufman, and T. Lee, ``Globally Asymptotically Stable Attitude Observer on SO(3),'' \textit{Proceedings of the 54th IEEE Conference on Decision and Control}, pp. 2164-2168, Osaka, Japan, December 2015.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Nonlinear Observability Measure for Relative Orbit Determination with Angles-Only Measurements,'' \textit{Proceedings of the 25th AAS/AIAA Space Flight Mechanics Meeting}, Williamsburg, VA, Jan. 2015, AAS 15-451.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Minimum Uncertainty JPDA Filter and Coalescence Avoidance Performance Evaluations,'' \textit{Proceedings of the 25th AAS/AIAA Space Flight Mechanics Meeting, Williamsburg}, VA, Jan. 2015, AAS 15-432.
	\item E. Kaufman, K. Caldwell, D. Lee, and T. Lee, ``Design and Development of a Free-Floating Hexrotor UAV for 6-DOF Maneuvers,'' \textit{Proceedings of the IEEE Aerospace Conference}, Mar. 2014, ASC 14-2527.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Optimal Joint Probabilistic Data Association Filter Avoiding Coalescence in Close Proximity,'' \textit{Proceedings of the European Control Conference}, pp. 2709-2714, June 2014.
	\vspace*{0.5cm}
\end{itemize}
}
\end{frame}

>>>>

\begin{frame}
\frametitle{Motivation and Goal}

\begin{itemize}
	\item Multiple agents can accomplish tasks faster and more reliably than a single agent
	\item Large groups are capable of coverage in large environments
	\item Problem: multi-vehicle map information gain optimality can be computationally intractable
	\item Solution: bidding-based solution simplifies a complicated optimization into a series of simplified optimizations
\end{itemize}

\begin{frame}
\frametitle{Related Work}

\begin{itemize}
	\item Most existing bidding-based techniques deal with auctioning tasks among a few agents locally in decentralized frameworks
	\item The other approach is for a central executive to run a series of auctions
	\item Bids are discounted between auctions to coordinate the efforts based on coverage overlap
	\item Heuristic, ad hoc
\end{itemize}

\begin{frame}
\frametitle{Proposed Approach}

\begin{itemize}
\item Central executive completes $n$ auctions for $n$ robots
\begin{enumerate}
	\item Each robot determines its optimal future pose, and bids the objective function
	\item The winner is awarded this future pose, and the remaining robots update their bids according to
	\begin{itemize}
		\item New expected map changes from the winner
		\item Collision-avoidance with the winner
	\end{itemize}
	\item Repeat these steps with the remaining robots
\end{enumerate}
\item The efforts are coordinated by updating bids between auctions
\end{itemize}
\end{frame}

% TODO: uncomment!
%\begin{frame}
%\frametitle{Numerical Example: SEH Second Floor}
%
%
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=Multi-Vehicle Mapping and Exploration.mp4,
%  		flashvars={source=Multi-Vehicle Mapping and Exploration.mp4}
%		]{}{VPlayer.swf}
%		}
%
%
%\end{frame}

@@

\begin{frame}
\frametitle{Publications on Dissertation Topics}
{\tiny 
\begin{itemize}
	\item E. Kaufman, K. Takami, T. Lee, and Z. Ai, ``Multi-Vehicle Cooperative Exploration and Patrol of Uncertain 3D Environments'', in preparation.
	\item E. Kaufman, K. Takami, T. Lee, and Z. Ai, ``Bidding-Based Autonomous Exploration of Cooperative Robots Building a 3D Probabilistic Occupancy Grid Map'', in preparation.
	\item E. Kaufman and T. Lee, ``Autonomous Aerial Exploration for Topological Mapping of Mars Environments'', \textit{2019 AIAA Guidance, Navigation, and Control Conference}, San Diego, CA, January 2019, submitted.
	\item E. Kaufman, K. Takami, Z. Ai, and T. Lee, ``Autonomous Quadrotor 3D Mapping and Exploration Using Exact Occupancy Probabilities,'' \textit{The Second IEEE International Conference on Robotic Computing}, pp. 49--55, Laguna Hills, CA, January 2018.
	\item E. Kaufman, K. Takami, T. Lee, and Z. Ai, ``Autonomous Exploration with Exact Inverse Sensor Models,'' \textit{Journal of Intelligent }\&\textit{ Robotic Systems}, 2017, doi: 10.1007/s10846-017-0710-7.
	\item E. Kaufman, T. Lee, and Z. Ai, ``Autonomous Exploration by Expected Information Gain from Probabilistic Occupancy Grid Mapping,'' \textit{IEEE International Conference on Simulation, Modeling, and Programming for Autonomous Robots}, pp. 246--251, San Francisco, CA, December 2016.
	\item E. Kaufman, T. Lee, Z. Ai, and I. S. Moskowitz, ``Bayesian Occupancy Grid Mapping via an Exact Inverse Sensor Model,'' \textit{Proceedings of the American Control Conference}, pp. 5709-5715, Boston, MA, July 2016.
\end{itemize}
}
\end{frame}

\begin{frame}
\frametitle{Publications on Data Association, Estimation, and Control}
{\tiny 
\begin{itemize}
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Nonlinear Observability Measure for Relative Orbit Determination with Angles-Only Measurements,'' \textit{The Journal of the Astronautical Sciences}, 63(1): pp. 60-80, 2016, doi: 10.1007/s40295-015-0082-9.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Minimum Uncertainty JPDA Filters and Coalescence Avoidance for Multiple Object Tracking,'' \textit{The Journal of the Astronautical Sciences}, 63(4): pp. 308-334, 2016, doi: 10.1007/s40295-016-0092-2.
	\item T. Wu, E. Kaufman, and T. Lee, ``Globally Asymptotically Stable Attitude Observer on SO(3),'' \textit{Proceedings of the 54th IEEE Conference on Decision and Control}, pp. 2164-2168, Osaka, Japan, December 2015.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Nonlinear Observability Measure for Relative Orbit Determination with Angles-Only Measurements,'' \textit{Proceedings of the 25th AAS/AIAA Space Flight Mechanics Meeting}, AAS 15-451, Williamsburg, VA, January 2015.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Minimum Uncertainty JPDA Filter and Coalescence Avoidance Performance Evaluations,'' \textit{Proceedings of the 25th AAS/AIAA Space Flight Mechanics Meeting, Williamsburg}, AAS 15-432, VA, January 2015.
	\item E. Kaufman, K. Caldwell, D. Lee, and T. Lee, ``Design and Development of a Free-Floating Hexrotor UAV for 6-DOF Maneuvers,'' \textit{Proceedings of the IEEE Aerospace Conference}, ASC 14-2527, March 2014, Big Sky, MT.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Optimal Joint Probabilistic Data Association Filter Avoiding Coalescence in Close Proximity,'' \textit{Proceedings of the European Control Conference}, pp. 2709-2714, Strasbourg, June 2014.
\end{itemize}
}
\end{frame}
